Wildcard: Spreadsheet-Driven Customization of Web Applications

### 2020-01-10 paper.tex
start designing the web version

For an online version of this paper with videos demonstrating the interface, see \url{https://www.geoffreylitt.com/wildcard/}
\end{abstract}

@@

>>>>

This paper is best viewed in the online version, which includes videos demonstrating the interface: \url{https://www.geoffreylitt.com/wildcard/}
\end{abstract}

@@

\begin{figure}
\hypertarget{fig:overview}{%
\centering
\includegraphics{media/overview-300dpi.png}
\caption{An overview of spreadsheet-driven
customization}\label{fig:overview}
}
\end{figure}
